|

### 2025-01-31 doc/paper.qmd
task 1 text

# Task 3 - Cross-Country Replication {#sec-task3}
Task 3 extends the analysis beyond the United States by replicating Figure 1 using 1972-2023 data (if entire data range pull possible) from a non-U.S. market, providing insights into how earnings informativeness varies across different regulatory environments and market structures. This task requires mapping variables from CRSP/Compustat to their equivalents in Worldscope/Datastream, adjusting for differences in accounting standards, market liquidity, and institutional factors. Worldscope (Thomson/Refinitiv) serves as the international alternative of Compustat for earnings announcement data, while Datastream provides stock market data for non-U.S. companies. While the core replication methodology remains the same, careful data handling and economic interpretation are crucial to account for cross-country analysis with Canada.

@@

Canada as the country of choice was influenced by the alignment with the methodology of @ball_how_2008, where the key factor in the selection was the availability of quarterly earnings reports, which ensures comparability with U.S. data. For Canada, the reporting frequency is majority 4x, with some 2x, similar to the US [@short_short_2025]. While Canada has a smaller market size than the U.S., its regulatory environment, reporting frequency, and institutional settings are highly comparable, making it an optimal choice for the non-U.S. analysis. Additionally, Canada features a developed capital market with high trading volume and liquidity, ensuring that stock price reactions to earnings announcements are observable in the replication. A further advantage is that Canadian firms registered with the U.S. Securities and Exchange Commission (SEC) can report under U.S. GAAP, making their financial disclosures fully compatible with U.S. firms. This reduces methodological differences to the original study.

@@

1. To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency. Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets demands modular approach. Therefore, I isolate the workflow for @sec-task3 into working files `...-wscp`, thus reducing complicated dependencies across tasks.

@@

3. I verified whether Worldscope and Datastream follow the same earnings announcement date convention as Compustat or if they report earnings based on fiscal periods. I decided to use Worldscope items 5901–5904 from historical stock-related data in `wrds_ws_stock`, which represent the actual date when a company publicly reports its earnings for each quarter, where, however, data for these fields is generally not available prior to 1992. [@thomson_financial_worldscope_2007, p.281]. This may cause limited data sample size.

@@

5. Similar to @sec-task1, I use returns `ret` variable in Datastream to simplify the process, presented as percentage change. Bid and ask prices are ignored.

@@

## Replication Steps {#sec-replication_steps3}
Same as in @sec-task1 the analysis involves gathering and filtering stock return and earnings announcement data, linking Datastream stock data with WSCP (Worldscope), and estimating the relationship between annual returns and earnings-announcement window returns. The replication process follows a structured workflow of data pull, preparation, and analysis, ensuring consistency with the original study.

@@

The data pull step retrieves quarterly earnings announcement dates from Worldscope and daily stock returns from Datastream, filtering for Canadian firms from 1980 onward. The datasets are saved separately and later merged using firm-level identifiers. Only common equity (`typecode` = EQ) is included to ensure consistency with CRSP.

@@

If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample. This filtering step removed 3,609,492 missing firm-year observations. Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year. The final dataset consists of only 616,980 valid firm-year observations, starting in 1996 only, signaling the potential difference in the accounting reporting standards between the U.S. and Canada.

Notably, after pulling the annual stock data for further annual return calculation, all infocodes present an average of 250 trading days, highlighting full year stock coverage.

**Step 3: Analysis Implementation and Reproduction of Tables and Figure**

>>>>

# Task 3 - Cross-Country Replication {#sec-task3}
Task 3 extends the analysis beyond the U.S. by replicating Figure 1 using 1972–2023 data from a non-U.S. market, examining how earnings informativeness varies across regulatory environments and market structures. This requires mapping CRSP/Compustat variables to their Worldscope/Datastream equivalents while adjusting for accounting standards, market liquidity, and institutional factors. Worldscope provides earnings announcement data, and Datastream covers stock returns. While the core methodology remains, careful data handling and interpretation are essential for cross-country analysis, particularly with Canada.

@@

Canada was chosen for its quarterly reporting frequency, ensuring comparability with U.S. data, as most firms report four times per year, with some semi-annual reports [@short_short_2025]. Despite its smaller market size, Canada’s regulatory environment, liquidity, and institutional settings closely align with the U.S., making it an ideal candidate. Additionally, Canadian firms registered with the SEC can report under U.S. GAAP, making their financial disclosures fully compatible with U.S. firms.

@@

1. To ensure a smooth and conflict-free process, I handle the WSCP/Datastream workflow separately, preventing potential interference with the CRSP/Compustat pull process and improving debugging efficiency. Although a unified pull/prepare/do_analysis file for all databases would be ideal and streamline management, the large-scale nature of the extracted datasets demands modular approach.

@@

3. I verified whether Worldscope and Datastream follow the same earnings announcement date convention as Compustat or if they report earnings based on fiscal periods. I decided to use Worldscope items 5901–5904 from historical stock-related data in `wrds_ws_stock`, which represent the actual date when a company publicly reports its earnings for each quarter, where, however, data for these fields is generally not available prior to 1992 [@thomson_financial_worldscope_2007, p.281]. This may cause limited data sample size.

@@

5. Similar to @sec-task1, I use returns `ret` variable in Datastream for returns, presented as percentage change. Bid and ask prices are ignored.

@@

## Replication Steps {#sec-replication_steps3}
The process is same as in @sec-task1.

@@

Next, retrieve quarterly earnings announcement dates from Worldscope and daily stock returns from Datastream, filtering for Canadian firms from 1980 onward. The datasets are saved separately and later merged using firm-level identifiers. Only common equity (`typecode` = EQ) is included to ensure consistency with CRSP.

@@

If a firm had missing values for any of the Earnings Per Share Report Date fields (item5901–item5904), it did not meet the criteria set by @ball_how_2008 and was excluded from the sample. This filtering step removed 3,609,492 missing firm-year observations. Additionally, 5,996,793 firm-year entries were dropped because their four earnings announcements did not fall within the same calendar year. Furthermore, I extend dynamically shift the missing values for trading days -1,0,1 within 3 day window, due to small sample size to keep more earning announcemnet windows.

From this cleaned dataset, BHR event returns are computed. Then, annual stock returns for the firms of the filtered sample are extracted from Datastream pulled data . Finally, the Annual BHR Returns are calculated. Notably, after pulling the annual stock data for further annual return calculation, all infocodes present an average of 250 trading days, highlighting full year stock coverage.

**Step 3: Analysis Implementation and Reproduction of Tables and Figure**  
I conduct the earnings informativeness analysis by computing summary statistics (Table 1), running annual regressions (Table 2), and generating a replication of Figure 1. First, I loaded the computed event-window and annual buy-and-hold returns (BHR_3day, BHR_Annual) and produced summary statistics similar to @ball_how_2008. Next, I performed annual cross-sectional regressions of stock returns on earnings-announcement returns, benchmarking against an Abnormal R² (adjusted R² minus 4.8%), while handling missing data and ensuring a valid number of observations per year. Finally, the script plots Figure 1, visualizing Abnormal R² trends (Panel A) and slope coefficients (Panel B) over time, saving it as both a PNG and a pickle file for further use.
